---
title: "skincare package"
author: "Ruyue Zhang"
date: "November 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## package description
This package is designed for data collected from a survey which contains many character catgorical variables or other similar dataset. 

This package helps to summary data and do some basic analysis. When dealing with data collected from survey, the most time-comsuming thing is to recode data. This package contains a function to simplify the recoding process. Also, sometimes we need to conduct t-test to several variables with a same variable. For example, we often need to decide whether age would make a significant difference to some variables. By using this function in the package, we can finish the process by a single function instead of doing it repeatedly.

##Note: All examples below uses the data from skin-care preference survey
```{r}
#import data directly from Googlesheet
library(googlesheets)
egdata<-gs_url("https://docs.google.com/spreadsheets/d/1sGAW3lR6KZOSsPVkJ40CQqeUQtLku-cgvCf81sY-2Es/edit?usp=sharing")
egdata<-gs_read(egdata)
egdata<-as.data.frame(egdata)
colnames(egdata)<-c("submit-time","gender","age","income","money spent","skin-type","numberofproducts_day", "aspect","suncare_frequency","skincare-frequency","","condition","age_start","time_skincare_day","makeup-fre","")

```

## Introduction of functions
## 1. Function: recodecatvar
Usage: recodecatvar(x, d, y, z)

description:Recode character catgorical variables into numeric variables.

Arguments:
x(numeric): number of categories within this column
d(data.frame): the dataset 
y(numeric): the column to be recoded
z(vector): a vector contains all the catgory names of the variable

Example: 
Recode gender, skin-type and age in skincare-preference data
```{r}
library(skincare)
print(egdata[1:10,])

catname.gender<-c("female","male","other")
egdata<-recodecatvar(3,egdata,2,catname.gender) #recode gender


catname.age<-c("below 20","20s","30s","40s","above 50")
egdata<-recodecatvar(5,egdata,3,catname.age) #recode age

catname.type<-c("dry","normal","oily","combinational","sensitive")
egdata<-recodecatvar(5,egdata,6,catname.type) #recode skin-type

print(egdata[1:10,])

```

## 2. Function: multittest
Usage: multittest(x, y, z)

Description: This function is designed to do t-test to several variables with a same variable.

(More details: see the help file of multittest)

Example: 
Do t-test i)between age and skintype
          ii)between gender and skintype
```{r}
library(skincare)
coln<-c(2,3)
multittest(egdata,6,coln)
```
