---
title: "skincare package"
author: "Ruyue Zhang"
date: "November 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## package description
This package is designed for data collected from a survey which contains many character catgorical variables.

This package helps to summary data and do some basic analysis. When dealing with data collected from survey, the most time-comsuming thing is to recode data. This package contains a function to simplify the recoding process. Also, sometimes we need to conduct t-test to several variables with a same variable. By using this function in the package, we can finish the process by a single function instead of doing it repeatedly.

##Note: All examples below uses the data from skin-care preference survey
```{r}
#import data directly from Googlesheet
library(googlesheets)
egdata<-gs_url("https://docs.google.com/spreadsheets/d/1sGAW3lR6KZOSsPVkJ40CQqeUQtLku-cgvCf81sY-2Es/edit?usp=sharing")
egdata<-gs_read(egdata)
egdata<-as.data.frame(egdata)
colnames(egdata)<-c("submit-time","gender","age","income","money spent","skin-type","numberofproducts_day", "aspect","suncare_frequency","skincare-frequency","","condition","age_start","time_skincare_day","makeup-fre","")

```

## Introduction of functions
## 1. Function: summary.pie
Usage: summary.pie(x,y)

Description: This function is used to get pie chart of catgorical variables

(More details: see the help file of summary.pie)

Example: get summary chart of gender and age in skin-care preference data

```{r}
library(skincare)
summary.pie(egdata,2)
summary.pie(egdata,3)
```


## 2. Function: recodecatvar
Usage: recodecatvar(x, d, y, z)

Description:Recode character catgorical variables into numeric variables.

(More details: see the help file of recodecatvar)

Example: 
Recode gender, skin-type and age in skincare-preference data
```{r}
library(skincare)
print(egdata[1:10,])

catname.gender<-c("female","male","other")
egdata<-recodecatvar(3,egdata,2,catname.gender) #recode gender


catname.age<-c("below 20","20s","30s","40s","above 50")
egdata<-recodecatvar(5,egdata,3,catname.age) #recode age

catname.type<-c("dry","normal","oily","combinational","sensitive")
egdata<-recodecatvar(5,egdata,6,catname.type) #recode skin-type

print(egdata[1:10,])

```

## 3. Function: multittest
Usage: multittest(x, y, z)

Description: This function is designed to do t-test to several variables with a same variable.

(More details: see the help file of multittest)

Example: 
Do t-test i)between age and skintype
          ii)between gender and skintype
```{r}
library(skincare)
coln<-c(2,3)
multittest(egdata,6,coln)
```
